---
title: "DDP Presentation"
author: "PK"
date: "16/01/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

- Presentation is part of the project assignment for Coursera Developing Data Products class. 
- Purpose of the project is to write a shiny app that can help predict car MPG based on weight and transmission.
- This presentation will explain the app features. 

## Miles per Gallon vs cylinder
This plot shows how the MPG varies depending on the number of cylinders and the type of transmission.
By selecting the car transmission (automatic or manual) the figure displays the distribution of MPG for 4,6, and 8 cylinder cars.
```{r}
boxplot(mpg~cyl, data = mtcars, col="blue",
                main="Miles per Gallon vs Number of Cylinders",
                ylab="Miles per Gallon",
                xlab="Number of Cylinders")
```


## Miles per Gallon vs Weight

- Scatterplot shows how the MPG vary depending on the vehicle weight and the type of transmission.
- By selecting the car transmission type (automatic or manual), the plot displays the value of MPG for each weight and a regression line is also provided.
- After selecting the transmission in the dropdown menu and the car weight in the slider, the predicted MPG is displaid based on the linear regression model.

## Miles per Gallon vs Weight Plot

```{r lm, echo=FALSE}
plot(mtcars$wt, mtcars$mpg, main = "Miles per Gallon vs Weight",
     xlab = "Weght (lb/1000)", ylab = "Miles per Gallon", pch=16)
abline(lm(mpg~wt,data = mtcars)) 
```

